LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2021-11-19 src/ms.tex
change equation, add note, acknowledge

\subsubsection{TianQin}
For the TianQin sensitivity curve we use the power spectral density given in \citet[][Eq.~13]{Huang+2020}
\begin{equation}{\lwFuncURL{psd}{tianqin_psd}}
    \begin{split}
    S_{N}(f) &= \frac{1}{L^{2}}\left[\frac{4 S_{a}}{(2 \pi f)^{4}}\left(1+\frac{10^{-4} \unit{Hz}}{f}\right)+S_{x}\right] \\
    & \times\left[1+0.6\left(\frac{f}{f_{*}}\right)^{2}\right],
    \end{split}
\label{eq:tianqin}
\end{equation}
where $L = \sqrt{3} \times 10^5 \unit{km}$ is the arm length, $S_a = 1 \times 10^{-30} \unit{m^2}{s^{-4}}{Hz^{-1}}$ is the acceleration noise, $S_x = 1 \times 10^{-24} \unit{m^2}{Hz^{-1}}$ is the displacement measurement noise and $f_* = c / 2 \pi L$ is the transfer frequency.

@@

\begin{acknowledgements}
    % People
    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project. We thank the BinCosmos group for testing an early version of the package and providing useful feedback. In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}!  TW thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation. KB thanks Shane L. Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation.

>>>>

\subsubsection{TianQin}
For the TianQin sensitivity curve we use the power spectral density given in \citet[][Eq.~13]{Huang+2020}
\begin{equation}{\lwFuncURL{psd}{tianqin_psd}}
    \begin{split}
    S_{N}(f) &= \frac{10}{3 L^{2}}\left[\frac{4 S_{a}}{(2 \pi f)^{4}}\left(1+\frac{10^{-4} \unit{Hz}}{f}\right)+S_{x}\right] \\
    & \times\left[1+0.6\left(\frac{f}{f_{*}}\right)^{2}\right],
    \end{split}
\label{eq:tianqin}
\end{equation}
where $L = \sqrt{3} \times 10^5 \unit{km}$ is the arm length, $S_a = 1 \times 10^{-30} \unit{m^2}{s^{-4}}{Hz^{-1}}$ is the acceleration noise, $S_x = 1 \times 10^{-24} \unit{m^2}{Hz^{-1}}$ is the displacement measurement noise and $f_* = c / 2 \pi L$ is the transfer frequency. Note that Eq.~\ref{eq:tianqin} includes an extra factor of $10 / 3$ compared to \citet[][Eq.~13]{Huang+2020}. \citet{Huang+2020} absorb this factor into the waveform rather than include it in the power spectral density. We include it to match the convention used by \citet{Robson+2019} for the LISA sensitivity curve (see the factor of $10/3$ in Eq.~\ref{eq:LISA_Sn}) so that the sensitivity curves can be compared fairly.

@@

\begin{acknowledgements}
    % People
    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Yi-Ming Hu, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project. We thank the BinCosmos group for testing an early version of the package and providing useful feedback. In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}!  TW thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation. KB thanks Shane L. Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation.
